Spfy: an integrated graph-based sequence database for real-time prediction of Escherichia coli phenotypes

### 2018-01-31 paper-webserver.tex
EDIT: some changes to the web design paragraph

@@

The front-end website is written using the React JavaScript library \url{https://facebook.github.io/react/} as a single-page application to allow efficient data-flow without reloading the website.
To ensure a familiar user interface, we followed the Material Design specification \url{https://material.io/}, published by Google, surrounding a card-based design.
(see Figure \ref{fig-results})
Both the task selection and result displays follow this card-based design: while data storage is graph-based, the results of various analysis modules are presented to users in a familiar tabular structure and available for download as .csv spreadsheet files.
(see Figure \ref{fig-tables})

>>>>

% TODO: add figure illustrating search.

@@

The front-end website is written using the React JavaScript library \url{https://facebook.github.io/react/} as a single-page application resembling a traditional desktop application.
To ensure a familiar user interface, we followed the Material Design specification \url{https://material.io/}, published by Google, surrounding a card-based design.
(see Figure \ref{fig-results})
Both the task selection and result displays follow the same design pattern: while data storage is graph-based, the results of various analysis modules are presented to users in a familiar tabular structure and available for download as .csv spreadsheet files.
(see Figure \ref{fig-tables})
